Concurrent Programming with CXL

### 2020-06-05 book/paper.tex
Latest

It is instructive to see what happens when a writer is in the critical
section and two readers try to enter.  The first reader successfully
acquires \texttt{rlock} and but \emph{hangs} when trying to acquire
\texttt{rwlock}, which is held by the writer.  The second reader hangs
trying acquire \texttt{rlock} because it is held by the first reader.
When the writer leaves the critical section, the first reader acquires
\texttt{rwlock}, sets \texttt{nreaders} to 1, and releases \texttt{rlock}.
\texttt{rwlock} is still held.
Then the second reader acquires \texttt{rlock} and, assuming the first
reader is still in the critical section, increments \texttt{nreaders} to 2
and enter the critical section \emph{without} acquiring \texttt{rwlock}.
\texttt{rwlock} is essentially jointly held by both readers.
It does not matter in which order they leave: the second will release
\texttt{rwlock}.

@@

\begin{quote}
\begin{itemize}
\item Why do you suppose the code in Figure~\ref{fig:rwmulti} uses a flag
per process rather than a simple counter?
\item Can you write a version of this test that uses a counter instead
of a flag per process?
\end{itemize}
\end{quote}

>>>>

It is instructive to see what happens when a writer is in the critical
section and two readers try to enter.  The first reader successfully
acquires \texttt{rlock} and but blocks (!) when trying to acquire
\texttt{rwlock}, which is held by the writer.  The second reader blocks
trying acquire \texttt{rlock} because it is held by the first reader.
When the writer leaves the critical section, the first reader acquires
\texttt{rwlock}, sets \texttt{nreaders} to 1, and releases \texttt{rlock}.
\texttt{rwlock} is still held.
Then the second reader acquires \texttt{rlock} and, assuming the first
reader is still in the critical section, increments \texttt{nreaders} to 2
and enter the critical section \emph{without} acquiring \texttt{rwlock}.
\texttt{rwlock} is essentially jointly held by both readers.
It does not matter in which order they leave: the second will release
\texttt{rwlock}.

@@

\begin{quote}
\begin{itemize}
\item Why do you suppose the code in Figure~\ref{fig:rwmulti} uses a flag
per process rather than a simple counter?
\item Can you write a version of this test that uses a counter instead
of a flag per process?
\item Write a ``library implementation'' of reader/writer locks so multiple
reader/writer locks can be instantiated.
\end{itemize}
\end{quote}
